Исследование доступности информационных сервисов для мобильных пользователей

### 2013-09-12 summary.tex
Поменялись аннотация и реферат на английском языке

\renewcommand{\baselinestretch}{1.13}

@@

Feature of mesh networks is dynamically change the topology and the absence of a priori information about the location of points of access to the cloud, which determines the possible presence of a number of different ways to deliver information messages.

The primary means of research the behavior of mesh networks is simulation, which allows scripts to perform various behaviors mesh networks. In this work, a model was developed automotive mesh network implemented on the basis of a model of traffic IDM means of discrete-event simulation of computer networks ns--3.

Analysis of simulation results showed that the use of the automobile mesh network significantly increases the availability of cloud services while sharing emergency messages in a variety of configurations automotive mesh network, network traffic characteristics and peculiarities of traffic.
}

>>>>

\renewcommand{\baselinestretch}{1.2}

@@

The feature of mesh-networks is dynamically changing topology and absence of a priory information about arrangement of cloud environment access points, all of which defines possible existence of many different routes for information messages delivery.

The main method of analysis of the behavior of mesh-networks is simulation which allows to perform different scenarios of mesh-network behavior without implementation of full-scale experiment. Within the bounds of this work the model of automotive mesh-network was developed on basis of IDM traffic model and implemented through NS-3 discrete-event simulator of computer networks.

Analysis of simulation results has revealed that use of automotive mesh-network substantially increases availability of emergency messages exchange cloud services in different configurations of automotive mesh network, network traffic properties and road traffic characteristics.
}
